---
title: "Supplement to Application for Dir. Childcare Analytics, BESP"
resource_files:
- ZIP_CODE_040114/ZIP_CODE_040114.shp.xml
- ZIP_CODE_040114/ZIP_CODE_040114.dbf
- ZIP_CODE_040114/ZIP_CODE_040114.sbn
- ZIP_CODE_040114/ZIP_CODE_040114.sbx
- ZIP_CODE_040114/ZIP_CODE_040114.shp
- ZIP_CODE_040114/ZIP_CODE_040114.shx
- ZIP_CODE_040114/ZIP_CODE_040114.prj
- ZIP_CODE_040114/ZIP_CODE_040114.shp.xml
- ZIP_CODE_040114/ZIP_CODE_040114.dbf
- ZIP_CODE_040114/ZIP_CODE_040114.sbn
- ZIP_CODE_040114/ZIP_CODE_040114.sbx
- ZIP_CODE_040114/ZIP_CODE_040114.shp
- ZIP_CODE_040114/ZIP_CODE_040114.shx
- ZIP_CODE_040114/ZIP_CODE_040114.prj
- ZIP_CODE_040114/ZIP_CODE_040114.shp.xml
- ZIP_CODE_040114/ZIP_CODE_040114.dbf
- ZIP_CODE_040114/ZIP_CODE_040114.sbn
- ZIP_CODE_040114/ZIP_CODE_040114.sbx
- ZIP_CODE_040114/ZIP_CODE_040114.shp
- ZIP_CODE_040114/ZIP_CODE_040114.shx
- ZIP_CODE_040114/ZIP_CODE_040114.prj
runtime: shiny
output:
  flexdashboard::flex_dashboard:
    orientation: rows
    source_code: https://github.com/srand525/BESP_code_samples
    vertical_layout: scroll
---

```{r include = FALSE}
library(flexdashboard)
library(magrittr)
library(highcharter)
library(leaflet)
library(shiny)
options(shiny.sanitize.errors = FALSE)
```


# Introduction {.sidebar}

Select a date to view data gathered during inspections of childcare facilities.

```{r input_val}
dateInput("date1", "Inspection Date:", value = as.Date("2019-10-01"))
```



#### Data Sources

**Inspectional Data** 

Dataset Name: Childcare Center Inspections  
Data Provider: NYC Department of Health and Mental Hygiene (DOHMH)   
Accessed Via: [NYC Open Data](https://data.cityofnewyork.us/Health/DOHMH-Childcare-Center-Inspections/dsg6-ifza/data)   

**Shape files**    

Dataset Name: Zip Code Boundaries   
Data Provider: Department of Information Technology & Telecommunications (DoITT)   
Accessed Via: [NYC Open Data](https://data.cityofnewyork.us/Business/Zip-Code-Boundaries/i8iw-xf4u/data?no_mobile=true)   

**Zip Code Demographics Survey**   

Dataset Name: Demographic Statistics By Zip Code    
Data Provider: NYC Department of Youth and Community Development (DYCD)   
Accessed Via: [NYC Open Data](https://data.cityofnewyork.us/City-Government/Demographic-Statistics-By-Zip-Code/kku6-nxdu)  

_Note:_  

[DOHMH Childcare Center Inspections, NYC Open Data](https://data.cityofnewyork.us/Health/DOHMH-Childcare-Center-Inspections/dsg6-ifza/data)

Violations by Geography
=======================================================================

## Slider column

### Violations Found during Inspections {.value-box}

```{r num_viol}
source("agg_data.R",local = F)

num_violations <- reactive({violations_by_zip_demo %>%
  filter(inspection_date == input$date1) %>%
    summarise(tot_violations = sum(n_violations))
})

renderValueBox({
  valueBox(
    value = num_violations(),
    icon = "fa-exclamation-triangle",
    color = "blue"
  )
})
```

### Facilities with Violations {.value-box}

```{r num_fac}
source("agg_data.R",local = F)

num_facilities <- reactive({violations_by_zip_demo %>%
  filter(inspection_date == input$date1) %>%
    summarise(tot_facilities = sum(n_facilities))
})

renderValueBox({
  valueBox(
    value = num_facilities(),
    icon = "fa-school",
    color = "red"
  )
})
```


### Children Potentially Impacted {.value-box}

```{r num_kids}
source("agg_data.R",local = F)

num_children <- reactive({
  violations_by_reach %>% 
    filter(inspection_date == input$date1) %>% 
    summarise(kids = sum(tot_reach)) %>% select(kids)
})

renderValueBox({
  valueBox(
    value = format(num_children(),big.mark = ","),
    icon = "fa-child",
    color = "grey"
  )
})
```


### Zip Codes with Facilities Reporting Violations {.value-box}

```{r geo_valuebox}
source("agg_data.R",local = F)
source("map.R",local = F)

gen_shape_vals <- reactive({
  shape_test<-gen_shape_files(input_date = input$date1)
  length(unique(shape_test$ZIPCODE[!is.na(shape_test$n_violations)]))
})


renderValueBox({
  # num_zips(shape_test)
  valueBox(
    value = gen_shape_vals(),
    icon = "fa-area-chart",
    color = "green"
  )
})
```

Row
-----------------------------------------------------------------------

### Demographic data from NYC Open Data, Department of Youth and Community Development (DYCD)
```{r message=FALSE, warning=FALSE}
source("map.R",local = F)
source("agg_data.R",local = F)


gen_this_shape_file <- reactive({
  gen_shape_files(input_date = input$date1)
})


renderLeaflet({
  shape_test <- gen_this_shape_file()
  popup_test <- gen_popup(shape_test)
  colorramp_test <- gen_color_ramp(shape_test)
  map <- gen_map(shape_file = shape_test,color_ramp = colorramp_test,pop_up = popup_test)

  map
})

```


Violations by Inspection Date
=======================================================================

### Summary Trendline

```{r trend_line}
source("trendline.R",local = F)

hc_trendline
```

